---
title: "HW2 Telemarketing"
author: "Mark Bruno"
date: "3/24/2022"
output:
  html_document:
    toc: yes
    theme: readable
    highlight: tango
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Downloading and Prepping the Data

```{r}
#Downloading and Prepping the Data
tele <- read.csv("tele.csv", stringsAsFactors = TRUE)
summary(tele)

#We are deleting the "duration" and "X" variables because it is an after the fact measurement. We only should be using variables that we know before the call
tele$duration <- NULL

# Deleting the column X
tele$X <- NULL
tele$default <- NULL

set.seed(12345)
kill_rows <- sample(1:nrow(tele), 0.25*nrow(tele))
tele <- tele[kill_rows,]

# Changing pdays to a dummy and deleting pdays
tele$pdaysdummy <- ifelse(tele$pdays == 999, 0, 1)
tele$pdays <- NULL

str(tele)
```

## Getting Data Ready for Analysis

```{r}
# Using model.matrix to convert all the factors to dummy variables
# We are converting all of the factors into dummy variables as the input into ANN has to be numeric

telemm <- as.data.frame(model.matrix(~.-1,tele))
str(telemm)

# Randomize the rows in the data (shuffling the rows)
#set.seed(12345)
#tele_random <- telemm[sample(nrow(telemm)),]

#Normalize the data
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

# we are going to normalize everything 
tele_norm <- as.data.frame(lapply(telemm, normalize))
str(tele_norm)
```


## Getting Train and Test Samples

```{r}
# Selects 10000 random rows for test data
set.seed(12345)
test_set <- sample(1:nrow(tele_norm), 10000) 
# Depending on R-version and computer, different rows may be selected. 
# If that happens, results are different. 

# Create a train set and test set
#First the predictors - all columns except the yyes column
tele_train <- tele_norm[-test_set, ]
tele_test <- tele_norm[test_set, ]
str(tele_train)
summary(tele_train)
```
```{r}
str(tele_test)
summary(tele_test)
```

## Upsampling Training Data

```{r}

#upsampling 
library("caret")
set.seed(123)
tele_train1 <- upSample(tele_train[ ,-ncol(tele_train)], as.factor(tele_train$yyes))

summary(tele_train1)

#renaming column 

tele_train1$yyes <- as.numeric(tele_train1$Class)
summary(tele_train1)
tele_train1$Class <- NULL
tele_train1$yyes <- tele_train1$yyes

summary(tele_train1)

```



> Now you are ready to build your ANN model. Feel free to modify the data load, cleaning and preparation code above as per your preference.

```{r, cache=TRUE}
library(neuralnet)
model1 <- neuralnet(yyes ~ ., data = tele_train,stepmax = 1e8)
model2 <- neuralnet(yyes ~ ., data = tele_train, hidden = 5, stepmax = 1e8)
model3 <- neuralnet(yyes ~ ., data = tele_train, hidden = c(4,3,2), stepmax = 1e8)
```

```{r}
plot(model1)

```
```{r}
plot(model2)

```


```{r}
plot(model3)
```

## Predict Test Data

```{r}
p1 <- predict(model1, tele_test)
summary(p1)
```
```{r}
p1binary <- ifelse(p1 >= 0.5, 1, 0)

p2 <- predict(model2, tele_test)
summary(p2)
```
```{r}
p2binary <- ifelse(p2 >= 0.3, 1, 0)

p3 <- predict(model3, tele_test)
summary(p3)
```
```{r}
p3binary <- ifelse(p3 >= 0.3, 1, 0)
```

## Evaluate Model

```{r}
library(gmodels)
CrossTable(p1binary, tele_test$yyes, prop.chisq = F, prop.r = F, prop.c = F, prop.t = F)
```

```{r}
CrossTable(p2binary, tele_test$yyes, prop.chisq = F, prop.r = F, prop.c = F, prop.t = F)
```
```{r}
CrossTable(p3binary, tele_test$yyes, prop.chisq = F, prop.r = F, prop.c = F, prop.t = F)
```

```{r}
confusionMatrix(as.factor(test_label), as.factor(test_pred), positive = "1")
```




##  Conclusion

Given the result of the 3 ANN Models, Model 1 seems to predict False Negatives with highest accuracy, while Model 2 seems to predict False Positives with highest accuracy. Model 3 has more balance between sensitivity and specificity. Depending on what variable we are more interested in (i.e., predicting people who would buy but didn't), we would choose the model that is more tuned toward predicting the parameter of interest. 


